Visualizations for the manuscript

### 2022-05-12 metanalysis_visualization/manuscript_Figures.Rmd
issue on the meta random forest fix adding sqrt. results consistents accross methods

metafor::forest(model_meta_siteid,
                slab = trends_siteid$plotsLabel,
                plim = c(1, NA),
                order = "obs",
                cex=0.7,
                showweights = TRUE,
                header="Sites",
                xlab = "Mean of the coefficients",
                mlab="Overall effect")
dev.off()
#ggsave("figure2A_metaanalysis_persite.png", height = 20, width = 45, units = "cm")

forest.meta( x = model_meta_siteid)

@@

>>>>

metafor::forest(model_meta_siteid,
                slab = trends_siteid$plotsLabel,
                plim = c(1, NA),
                order = "obs",
                cex=0.7,
                showweights = TRUE,
                header="Sites",
                xlab = "Mean of the coefficients",
                mlab="Overall effect")
dev.off()
#ggsave("figure2A_metaanalysis_persite.png", height = 20, width = 45, units = "cm")
```

@@

## Forest plot meta library

### By site
```{r}
m.siteid <- metagen(TE = observed,
                 seTE = sqrt( var_boot ),
                 data = trends_siteid,
                 studlab = plotsLabel,
                 sm = "MN",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL")

summary(m.siteid)

forest.meta(m.siteid, 
            sortvar = TE,
            print.tau2 = FALSE,
            leftlabs = c("plotsLabel"))

forest.meta(m.siteid, layout = "JAMA")
```

### By country
```{r}
m.country <- metagen(TE = pred,
                 seTE = sqrt( se**2 ),
                 data = trends_country,
                 studlab = country,
                 sm = "MN",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL")

summary(m.country)

forest.meta(m.country, 
            sortvar = TE,
            print.tau2 = FALSE,
            leftlabs = c("Country"))

forest.meta(m.country, layout = "JAMA")
```
